---
title: 'Comparison: MatLab and Python script'
author: "Jens Roeser"
date: "11/09/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, include = TRUE, message = FALSE)
options(scipen=999) # turn of scientific notation
# Load some essential packages
library(tidyverse)
```


## Summary

The speech on and offsets extracted by the matlab and the python scripts are similar but not identical. The differences are distributed symmatrically around 0 with very few extreme outliers. 


## Comparison

```{r}
d <- read_delim("matpyonsets.txt", delim = "\t")
```

Number wav files:

```{r}
nrow(d)
```


Onset latency (matlab script):


```{r}
with(d, summary(mat.onset))
```


Onset latency (python script):

```{r}
with(d, summary(py.onset))
```


Offset (matlab script):

```{r}
with(d, summary(mat.offset))
```


Offset (python script):

```{r}
with(d, summary(py.offset))
```

\newpage 


The difference between the voice onset latencies and voice offsets extracted by the MatLab script and extracted by the Python script is shown in Figure \ref{fig:histogram}.

```{r histogram, fig.cap="\\label{fig:histogram}Histograms of the difference in speech on and offsets.", fig.width=6, fig.height=3}
d %>% pivot_longer(cols = ends_with("Diff")) %>%
  mutate(name = recode_factor(name,  onsetDiff = "Voice onsets",
                                     offDiff = "Voice offsets", .ordered = T)) %>%
  ggplot(aes(x = value)) +
  facet_wrap(~name) +
  geom_histogram() +
  theme_light() +
  labs(title = "Difference between MatLab and Python script", subtitle =  "(MatLab - Python)") +
  theme(strip.text = element_text(hjust = 0),
        panel.grid = element_blank())
```


